Turbulence in compact to giant HII regions

### 2021-10-28 strucfunc_paper.tex
Javier changes to 2021-10-28

\begin{figure*}
  \centering
  \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-A}
  \label{fig:strucfunc-fit-A}
  \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-B}
  \label{fig:strucfunc-fit-B}
  \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-C}
  \label{fig:strucfunc-fit-C}
  \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}
\end{figure*}

% \begin{figure*}
% \centering
% \begin{multicols}{3}
% \includegraphics[width=2in]{Figures/SFplots/604.pdf}\par
% \includegraphics[width=2in]{Figures/SFplots/595.pdf}\par
% \includegraphics[width=2in]{Figures/SFplots/346.pdf}\par
% \end{multicols}
% \begin{multicols}{3}
% \includegraphics[width=2in]{Figures/SFplots/Hubble V.pdf}\par
% \includegraphics[width=2in]{Figures/SFplots/Hubble X.pdf}\par
% \includegraphics[width=2in]{Figures/SFplots/tarantula.pdf}\par
% \end{multicols}
% \begin{multicols}{3}
% \includegraphics[width=2in]{Figures/SFplots/Carina.pdf}\par
% \includegraphics[width=2in]{Figures/SFplots/M8.pdf}\par
% \includegraphics[width=2in]{Figures/SFplots/OS.pdf}\par
% \end{multicols}
% \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line investigated in this work. The first two rows consider extragalactic regions while the last row shows galactic regions.}
% \label{fig:SFs}
% \end{figure*}

>>>>

\begin{figure*}
 \centering
 \begin{multicols}{3}
 \includegraphics[width=2in]{Figures/SFplots/604.pdf}\par
 \includegraphics[width=2in]{Figures/SFplots/595.pdf}\par
 \includegraphics[width=2in]{Figures/SFplots/346.pdf}\par
 \end{multicols}
 \begin{multicols}{3}
 \includegraphics[width=2in]{Figures/SFplots/Hubble V.pdf}\par
 \includegraphics[width=2in]{Figures/SFplots/Hubble X.pdf}\par
 \includegraphics[width=2in]{Figures/SFplots/tarantula.pdf}\par
 \end{multicols}
 \begin{multicols}{3}
 \includegraphics[width=2in]{Figures/SFplots/Carina.pdf}\par
 \includegraphics[width=2in]{Figures/SFplots/M8.pdf}\par
 \includegraphics[width=2in]{Figures/SFplots/OS.pdf}\par
 \end{multicols}
 \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line investigated in this work. The first two rows consider extragalactic regions while the last row shows galactic regions.}
 \label{fig:SFs}
\end{figure*}
